---
title: "Wallace"
author: "Wallace Cordeiro"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      warning = F,
                      message = F)

setwd("/Users/Wallace/Desktop/Tese")
```

```{r libraries}
library(tidyverse)
library(texreg)
library(reshape2)
library(dplyr)
library(stringr)
library(lubridate)
library(corrplot)
library(car)
library(corrgram)
library(forecast)
library(stargazer)
library(Hmisc)
library(zoo)
library(dynlm)
library(broom)
library(knitr)
library(lmtest)
library(tseries)
library(fUnitRoots)
library(urca)
library(modelsummary)
source("/Users/Wallace/Desktop/Tese/Data/unit_resp_adl.R")
```

# Commodities

## Old commodities treatment

###Processing data

```{r}
comm_old <- read.csv("/Users/Wallace/Desktop/Tese/Data/us_monthlycommoditypriceindicesaverages_10570542104077_longold.csv", skip = 1, fileEncoding = "LATIN1")[-1,]

#reorganizing and subsetting the old file
comm_old <- comm_old %>% 
    rename(period=PRODUCT,
           comindex_current=Price.index...All.groups..in.terms.of.current.dollars.,
           comindex_constant=Price.Index...All.groups..in.terms.of.constant.dollars.,
           minerals=MINERALS..ORES.AND.METALS) %>% 
    mutate(period=as.Date(paste0("01",period), format = "%d%b%Y"))      %>% 
    select(period,comindex_current,comindex_constant,minerals)
```

## New Commodities treatment

### Processing data

Carregar arquivos e leve processamento

```{r}
comm_new <- read.csv("/Users/Wallace/Desktop/Tese/Data/us_commoditypriceindices_m_10600761997378_longnew.csv", skip = 1, fileEncoding = "LATIN1")[-1,]

#reorganizing and subsetting the new file
comm_new <- comm_new %>%
  rename(period=PRODUCT,
         comindex = All.groups,
         minerals=X..Minerals..ores.and.metals,
         minerals_nonprecious=X....Minerals..ores.and.non.precious.metals) %>% 
  mutate(period=as.Date(paste0("01",gsub("\\.?\\s","",gsub("June","Jun.",period))), format = "%d%b%Y"))  %>% 
  select(period,comindex,minerals,minerals_nonprecious)
```

## Merging all together

```{r}
comm <- merge(comm_old, comm_new, by = "period", all = T, suffixes = c("old",""))

comm$year <- year(comm$period)
comm$quarter <- quarter(comm$period)
comm$month <- month(comm$period)
```

### Correlogram new series

```{r}
plot(comm$period,comm$mineralsold,type="l",bty="n",ylab="",xlab="")
lines(comm$period,comm$minerals,col=gray(0.5),lty=2)
lines(comm$period,comm$minerals_nonprecious,col=gray(0.5),lty=3)
legend(x="topleft",
       legend=c("Minerals (old)","Minerals (new)","Minerals & Non-Precious (new)"),
       lty=c(1,2,3),
       col=c(1,gray(0.5),gray(0.5)),
       bty="n")

#coorelation coefficients
par(mar=c(1,1,1,1))
corrgram(subset(comm,select=c(comindex,comindex_current,
                              mineralsold,minerals,minerals_nonprecious)),
         upper.panel="panel.cor")

```

# Harmozining Old and New (minerals)

## Regressing the series

```{r}
the.reg <- lm(mineralsold~minerals_nonprecious, data=comm)#predict old index based on new index
pred <- predict(the.reg,newdata=data.frame(minerals_nonprecious=comm$minerals_nonprecious))
```

# Plot the series (only since 1990)

```{r}
par(mar=c(2,2,1,1))
start.plot <- which(comm$period=="1990-01-01")
plot(comm$period[start.plot:nrow(comm)],
     comm$mineralsold[start.plot:nrow(comm)]
     ,type="l",bty="n",ylab="",xlab="",ylim=c(0,500))
lines(comm$period[start.plot:nrow(comm)],
      comm$minerals_nonprecious[start.plot:nrow(comm)],col=gray(0.5),lty=3)
lines(comm$period[start.plot:nrow(comm)],
      pred[start.plot:nrow(comm)],col=3)
legend(x="topleft",
       legend=c("Minerals (old)","Minerals & Non-Precious (new)","Predicted minerals"),
       lty=c(1,2,1),
       col=c(1,gray(0.5),3),
       bty="n")

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/harmonized series.png")
dev.off()
```

## Creating new variable with the entire series

```{r}
comm$minerals_h <- ifelse(is.na(comm$mineralsold),
                          pred,comm$mineralsold)

```

Plot of the series old, new and harmonized

```{r}
comm %>% 
    pivot_longer(c(minerals_nonprecious, minerals, minerals_h)) %>% 
    ggplot(aes(x = period, y = value, color = name)) +
    geom_point()

comm %>% 
    ggplot(aes(x = period, y = minerals_h)) +
    geom_point() 

# CZ's plot
plot(comm$period,comm$minerals_h,type="l",lty=2,bty="n",xlab="",ylab="Index")
lines(comm$period,comm$mineralsold,col=gray(0.5))
lines(comm$period,comm$minerals_nonprecious,col=2)

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/oldandnewseries.png")
dev.off()
```

# HoS Approval Rates

```{r}
ead <- read.csv("/Users/Wallace/Desktop/Tese/Data/EAD 3.0 Beta Quarterly_07192023.csv")

#Separando o dados que quero
# Filter country
ead_c <- filter(ead, Country == "Australia")

#Creating columns with year and quarter
ead_c$year <- as.numeric(substr(ead_c$qtr, 1, 4))
ead_c$quarter <- as.numeric(substr(ead_c$qtr, 6, 6))

# Filter year
ead_c$year <- as.numeric(ead_c$year)

# Select only columns that we care about
ead_c <- select(ead_c, c(Country, qtr, Approval_Smoothed, year, quarter))

ead_c <- ead_c %>%
        select(Country, Approval_Smoothed, qtr, year, quarter) %>%
        rename(ead = Approval_Smoothed)

```

## Correlation between ead 2 and 3
```{r}
ead2 <- read.csv("/Users/Wallace/Desktop/Tese/Data/EAD+2.0+quarter+101019.csv")
ead2 <- filter(ead2, Country == "Australia")
ead2 <- ead2 %>%
        select(Country, qtr, Approval_Smoothed)
        names(ead2) <- c("country", "qtr", "ead2")
        
ead3 <- read.csv("/Users/Wallace/Desktop/Tese/Data/EAD 3.0 Beta Quarterly_07192023.csv")
ead3 <- filter(ead3, Country == "Australia")
ead3 <- ead3 %>%
        select(country_name, qtr, Approval_Smoothed)
        names(ead3) <- c("country", "qtr", "ead3")

eadcorr <- merge(ead2, ead3, by = c("qtr", "country"))      
corrgram(eadcorr, upper.panel = "panel.cor")

```


# Election and Head of Government

```{r}
leader <- read.csv("/Users/Wallace/Desktop/Tese/Data/leader_list_8_21 (1).csv")
leader <- filter(leader, stateabb == "AUL")
leader <- select(leader, stateabb, leader, sdate, smonth, syear, emonth, eyear)
leader$date <- as.Date(paste(leader$syear, leader$smonth, leader$sdate, sep = "-"))
leader$quarter <- quarter(leader$date)
#leader$qtr <- paste(leader$syear, leader$quarter, sep = "-") #num precisa mais
leader <- select(leader, leader, syear, quarter)
names(leader) <- c("leader", "year", "quarter")

election <- read.csv("/Users/Wallace/Desktop/Tese/Data/election_list_8_21.csv")
election <- election [, -(1:2)]
election <- filter(election, country == "Australia")
election$day <- ifelse(is.na(election$elec_day) | election$elec_day == "", 1, election$elec_day)
election$date <- as.Date(paste(election$elec_year, election$elec_month, election$day, sep = "-"))
election$quarter <- quarter(election$date)
election <- select(election, elec_year, quarter, event, victory, change)
names(election) <- c("year", "quarter", "type", "victory", "change")

```

# Domestic Variables

## GDP Growth

```{r}
gdp <- readxl::read_xlsx("/Users/Wallace/Desktop/Tese/Data/5206001_Key_Aggregates.xlsx", sheet = "Data1",skip = 9)
#gdp <- gdp[-c(1:9), ] ##remove the tag rows 
#moved this line above to "skip" in the previous one, so that it reads as date and numeric, respectively
gdp <- gdp[, c(1, 2)] ##just the gdp growth rate
names(gdp) <- c("date", "gdp_growth")
#gdp$date <- as.Date.numeric(as.numeric(gdp$date), origin = "1900-01-01")

gdp$year <- year(gdp$date) ##cria coluna com o mês numericamente
gdp$month <- month(gdp$date) ##cria coluna com o ano numericamente
gdp$quarter <- quarter(gdp$date) ##cria coluna com o quarter numericamente 

# you don't need day and date! you can merge by year and quarter, later!
```

## Inflation

```{r}
inf <- readxl::read_xlsx("/Users/Wallace/Desktop/Tese/Data/640101.xlsx", sheet = "Data1", skip = 9)
#inf <- inf[-c(1:9), ] ##remove tag rows
inf <- inf[, c(1, 28)] ##just the column with the inflation
names(inf) <- c("date", "inflation")
#inf$date <- as.Date.numeric(as.numeric(inf$date), origin = "1900-01-01")

inf$year <- year(inf$date) ##cria coluna com o mês numericamente
inf$month <- month(inf$date) ##cria coluna com o ano numericamente
inf$quarter <- quarter(inf$date) ##cria quarter 

```

## Unemployment rate MONTHLY

```{r}
unemp <- readxl::read_xlsx("/Users/Wallace/Desktop/Tese/Data/6202001.xlsx", sheet = "Data1")
unemp <- unemp[-c(1:9), ] ##remove the tag rows 
unemp <- unemp[, c(1, 65)] ##just the column with the percentage of unemployed 
names(unemp) <- c("date", "unemployment")
unemp$date <- as.Date.numeric(as.numeric(unemp$date), origin = "1900-01-01")

unemp$year <- year(unemp$date) ##cria coluna com o mês numericamente
unemp$month <- month(unemp$date) ##cria coluna com o ano numericamente
unemp$quarter <- quarter(unemp$date) ##cria coluna com o quarter

unemp$unemployment <- as.numeric(unemp$unemployment)
```


## Graphs
```{r}
domestic <- list(inf, gdp, unemp)
domestic <- Reduce(function(x, y) merge(x, y, by = c("year", "month", "quarter")), domestic)

domestic$inflation <- as.numeric(domestic$inflation)
domestic$gdp_growth <- as.numeric(domestic$gdp_growth)
domestic$unemployment <- as.numeric(domestic$unemployment)

domestic %>%
ggplot(aes(x = year, y = gdp_growth)) +
geom_point() +
geom_smooth() +
theme_bw() + 
xlab("year") + 
ylab("GDP Growth")
ggsave("gdp.jpeg", width = 9, height = 6)

all_data %>%
filter(year >= 1969) %>%
ggplot(aes(x = year, y = ead)) +
geom_point() +
geom_smooth() +
theme_bw() + 
xlab("year") + 
ylab("Popularity")
ggsave("pop.jpeg", width = 9, height = 6)
```


# Merging all QUARTERLY data

```{r}
# Create a list of the three quarterly data frames
# Keeping only the relevant variables
quarterly <- list(subset(inf,select=c(inflation,year,quarter)), 
                  subset(gdp,select=c(gdp_growth,year,quarter)),
                  subset(leader,select=c(leader,year,quarter)),
                  subset(election,select=c(type,victory,change,year,quarter)),
                  subset(ead_c,select=c(ead,year,quarter)))
              
quarterly <- Reduce(function(x, y) merge(x, y, by = c("year", "quarter")
                                         , all = TRUE), quarterly)

quarterly$qtr <- paste(quarterly$year,quarterly$quarter,sep="-")

quarterly <- quarterly %>%
  fill(leader, .direction = "down")

quarterly <- quarterly %>%
  mutate(election = ifelse(type == "Vote, As Scheduled" | type == "Vote, Early", 1, 0),
         election = ifelse(is.na(type), 0, election))

quarterly <- quarterly %>%
  mutate(early_vote = ifelse(type %in% c("Vote, Early"), 1, 0))

quarterly <- quarterly %>%
  rename(changeb = change)

quarterly <- quarterly %>%
  mutate(change = ifelse(leader == lag(leader), 0, 1))

quarterly <- quarterly %>%
  group_by(leader) %>%
  mutate(counter = ifelse(!is.na(leader), row_number(), NA))



```

# Merging all MONTHLY data and agreggating by quarter

```{r}
# Create a list of the monthly data frames
# Keeping only the relevant variables
monthly <- list(subset(unemp,select=c(unemployment,month,year,quarter)), 
                  subset(comm,select=c(minerals_h,month,year,quarter)))
monthly <- Reduce(function(x, y) merge(x, y, by = c("year","quarter","month")
                                         , all = TRUE), monthly)             
monthly$qtr <- paste(monthly$year,monthly$quarter,sep="-")

monthly_by_quarter <- monthly %>%
	        group_by(qtr) %>%
	        summarise(unemployment = mean(unemployment,na.rm=T),
	                  minerals_h = mean(minerals_h,na.rm=T))
```

# Merging the two data sets

```{r}
all_data <- merge(quarterly,monthly_by_quarter,by=c("qtr"),all=T)
save(all_data,file="data_wallace.RData")

corrgram(subset(all_data,
                select=c(inflation,gdp_growth,unemployment,
                          ead, minerals_h)))

```

# Corrgrams
```{r}
cordata <- all_data
cordata <- cordata[c("qtr", "year", "quarter", "inflation", "gdp_growth", "ead", "unemployment", "minerals_h", "minerals_d", "minerals_dpct", "okun_misery")]
names(cordata) <- c("qtr", "year", "quarter", "Inflation", "GDP_Growth", "Popularity", "Unemployment", "Commodityh", "Commoditydif", "Commodity_per", "Misery_Index")

datapre <- subset(cordata, year <2000)
corrgram(subset(datapre,select=c(Commodity_per,Misery_Index,GDP_Growth,Popularity))
         , main = "Pre-2000")

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/corrokunprior.png")
dev.off()

datapos <- subset(cordata, year >=2000)
corrgram(subset(datapos,select=c(Commodity_per,Misery_Index,GDP_Growth,Popularity))
         , main = "Post-2000")

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/corrokunpost.png")
dev.off()

corrgram(subset(cordata,
                select=c(Inflation,GDP_Growth,Unemployment,
                          Popularity, Commodityh)))
dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/mineralsHdom.png")
dev.off()

corrgram(subset(cordata,
                select=c(Inflation,GDP_Growth,Unemployment,
                          Popularity, Commoditydif)))
dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/mineralsDdom.png")
dev.off()

corrgram(subset(cordata,
                select=c(Inflation,GDP_Growth,Unemployment,
                          Popularity, Commodity_per)))
dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/mineralsDPCTdom.png")
dev.off()

```


# Creating diffs and lags

```{r}
# Lags para executive approval e para commodity price
all_data$ead_lag1  <- Lag(all_data$ead, shift = 1)
all_data$ead_lag2  <- Lag(all_data$ead, shift = 2)
all_data$minerals_h_lag1  <- Lag(all_data$minerals_h, shift = 1)
all_data$minerals_h_lag2  <- Lag(all_data$minerals_h, shift = 2)

all_data$minerals_d <- c(NA,diff(all_data$minerals_h))

all_data$minerals_dpct <- c(NA, diff(all_data$minerals_h)/
                              all_data$minerals_h[-nrow(all_data)]) * 100
all_data$minerals_dpct_lag1  <- Lag(all_data$minerals_dpct, shift = 1)
all_data$minerals_dpct_lag2  <- Lag(all_data$minerals_dpct, shift = 2)

all_data$hm <- all_data$counter<=2

# Lags para domestic variables
all_data$inflation_lag1  <- Lag(all_data$inflation, shift = 1)
all_data$inflation_lag2  <- Lag(all_data$inflation, shift = 2)

all_data$unemployment_lag1  <- Lag(all_data$unemployment, shift = 1)
all_data$unemployment_lag2  <- Lag(all_data$unemployment, shift = 2)

all_data$gdp_growth_lag1  <- Lag(all_data$gdp_growth, shift = 1)
all_data$gdp_growth_lag2  <- Lag(all_data$gdp_growth, shift = 2)

# Okum Misery Index
all_data$okun_misery <- all_data$inflation + all_data$unemployment
all_data$okun_misery_lag1  <- Lag(all_data$okun_misery, shift = 1)
all_data$okun_misery_lag2  <- Lag(all_data$okun_misery, shift = 2)


saveRDS(all_data, "datawallace.rds")
```


# Primary results
```{r}
approvalall <- lm(ead ~ minerals_dpct, data = all_data)
approval <- lm(ead ~ unemployment + gdp_growth + inflation, data = all_data)

punemp <- lm(unemployment ~ minerals_dpct, data = all_data)
pgdp <- lm(gdp_growth ~ minerals_dpct, data = all_data)
pinf <- lm(inflation ~ minerals_dpct, data = all_data)

stargazer(approvalall,
          title = "Executive Approval x Commodity Prices",
          align = TRUE, out = "primaryapprovalxcomm.tex", type = "latex")

stargazer(approval,
          title = "Executive Approval influenced by Domestic Variables",
          align = TRUE, out = "primaryapproval.tex", type = "latex")

stargazer(punemp, pgdp, pinf,
          title = "Domestic Economy Variables and Commodity Prices",
          align = TRUE, out = "primarydomcomm.tex", type = "latex")
```

```{r}
# Examine by PM term ####
by_pm <- all_data %>%
             group_by(leader) %>%
                summarise(
                  start = min(year),
                  in_office = n(),
                  av_growth = mean(gdp_growth,na.rm=T),
                  av_inflation = mean(inflation,na.rm=T),
                  av_unemployment = mean(unemployment,na.rm=T),
                  av_minerals = mean(minerals_h,na.rm=T),
                  av_dminerals = mean(minerals_dpct,na.rm=T),
                  av_pop = mean(ead,na.rm=T)) %>% 
             arrange(start)

by_pm <- subset(by_pm,in_office>1)
par(mfrow=c(1,2))
#plot(by_pm$av_minerals,by_pm$av_pop,cex=by_pm$in_office/20,
#      xlab="Average Minerals",ylab="Average Popularity")
#abline(reg=lm(av_pop~av_minerals,data=by_pm,weights=in_office))
plot(by_pm$av_dminerals,by_pm$av_pop,cex=by_pm$in_office/20,
     xlab="Average Pct Change in Minerals",ylab="Average Popularity")
abline(reg=lm(av_pop~av_dminerals,data=by_pm,weights=in_office))

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/000026.png")
dev.off()
```

# ADL TESTS
## ADL models for pct change in mineral (quarter over quarter)

```{r popminerals}

# Choose lag structure 
sel_data <- all_data

# Estimate all variantes of ADL(2,2) down to ADL(1,0)
adl22 <- lm(ead ~ ead_lag1 + ead_lag2 + 
                minerals_dpct + minerals_dpct_lag1 + minerals_dpct_lag2 +
                  hm + leader,data=sel_data)
adl21 <- lm(ead ~ ead_lag1 + ead_lag2 +  minerals_dpct + minerals_dpct_lag1 +
                  hm + leader,data=sel_data)
adl20 <- lm(ead ~ ead_lag1 + ead_lag2 +  minerals_dpct +
                  hm + leader,data=sel_data)
adl12 <- lm(ead ~ ead_lag1 +  minerals_dpct + minerals_dpct_lag1 + 
                  minerals_dpct_lag2 +
                  hm + leader,data=sel_data)
adl11 <- lm(ead ~ ead_lag1 + minerals_dpct + minerals_dpct_lag1 +
                  hm + leader,data=sel_data)
adl10 <- lm(ead ~ ead_lag1 + minerals_dpct +
                  hm + leader,data=sel_data)


# Collect
adls <- list(adl22=adl22,adl21=adl21,adl20=adl20
			,adl12=adl12,adl11=adl11,adl10=adl10)

# Compute residuals
adls.res <- lapply(adls,residuals)

# Check F tests for restricted version of ADL(2,2)
ff <- cbind(adl22=+Inf,
  adl21=linearHypothesis(adl22, "minerals_dpct_lag2=0", test= "F" )$Pr[2],
  adl20=linearHypothesis(adl22, c("minerals_dpct_lag2=0","minerals_dpct_lag1=0"), test= "F" )$Pr[2],
  adl12=linearHypothesis(adl22, "ead_lag2=0", test= "F" )$Pr[2],
  adl11=linearHypothesis(adl22, c("ead_lag2=0","minerals_dpct_lag2=0"), test= "F" )$Pr[2],
  adl10=linearHypothesis(adl22, c("ead_lag2=0","minerals_dpct_lag2=0","minerals_dpct_lag1=0"), test= "F" )$Pr[2]
)
rownames(ff)<-"ftest"

## Expanded diagnostics ##
# Unit Root: 
# Kwiatkowski-Phillips-Schmidt-Shin (KPSS) test for the null hypothesis that x is level or trend stationary: should *not* reject (p>=0.1).
# Phillips-Perron test for the null hypothesis that x has a unit root: should  reject (p<0.1).
# unitrootTest: based on McKinnons's test statistics. Null is unit root, should *reject* (p<0.1)
# Augmented Dickey-Fuller test (via adf.test): null is unit root: should *reject* (p<0.1)

# Serial correlation tests:",
# Breusch–Godfrey Lagr. mult. test. h0=No serial correlation up to p=2; *not reject* (p>=0.1)
# Durbin–Watson H statistic: h0=First order autocorrelation is 0, *not reject* (p>=0.1))
# Ljung–Box (‘portmanteau’) test statistic for examining the null hypothesis of independence in a given time series. (q.test replicates stata's)
library(lmtest)
library(tseries)
library(fUnitRoots)
tests <- rbind(
	kpss=sapply(adls.res,function(x){kpss.test(x)$p.value}),
	pp=sapply(adls.res,function(x){pp.test(x)$p.value}),
	urt = sapply(adls.res,function(x){unitrootTest(x,lags=1)@test$p.value[1]}),
	adf=sapply(adls.res,function(x){adf.test(x)$p.value}),
	bg=sapply(adls.res,function(x){bgtest(x~1
				,order=2,data=data.frame(res=x),fill=0)$p.value}),
	dw = sapply(adls,function(x){dwtest(lm(formula(x$call),data=x$model),
								alternative="two.sided")$p.value}) ,
	lbox=sapply(adls.res,function(x){Box.test(x, type="Ljung-Box")$p.value}),
	arIma=sapply(adls.res,function(x){auto.arima(x)$arma[c(1,2,6)]}),
	ftest=ff,
	bic=  sapply(adls,BIC))

out <- data.frame(t(tests))
names(out)[grep("^V",names(out))]<-c("ar","d","ma")
 
passed <- subset(out,ftest>0.1
						&kpss>=0.1
						&pp<0.1 
						&urt<0.1
						&adf<0.1
						&(bg>=0.1|dw>=0.1)
						&lbox>=0.1)
 
ss <- which(rownames(out)==rownames(passed)[which.min(passed$bic)])
selname <- rownames(passed)[which.min(passed$bic)]
cat("\nModel with lowest BIC among those (",nrow(out),") that passed all tests is ",selname,"\n",sep="")

```

# ADL model choosen (2,0)

## Variations in the selected model
````{r}
    # The selected model on full data
    reg1 <- lm(ead ~ ead_lag1 + ead_lag2 +minerals_dpct +
                      hm + leader,data=all_data)
    reg2 <- lm(ead ~ ead_lag1 + ead_lag2+ minerals_dpct +
                      leader,data=all_data)
    reg3 <- lm(ead ~ ead_lag1 + ead_lag2+ minerals_dpct +
                      hm,data=all_data)
    reg4 <- lm(ead ~ ead_lag1 + ead_lag2+ minerals_dpct
                      ,data=all_data)
    
par(mfrow=c(1,3)) 
acf(residuals(reg1))
pacf(residuals(reg1))
hist(residuals(reg1))
    
### THERE, DO A COMBINED TABLE FOR THE FOUR MODELS!!!!!  

out1 <- ur.effects(reg1, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out2 <- ur.effects(reg2, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out3 <- ur.effects(reg3, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out4 <- ur.effects(reg4, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")

par(mar=c(4, 4.5, 1, 1), mfrow=c(1, 1))
plot(c(0, 8), c(-1, 4), xlab="", ylab="", type="n", xaxt="n", bty="n", main="Full Sample")
axis(side=1, at=seq(0, 8, 1), labels=seq(0, 8, 1))
mtext("Quarters Since Shock", side=1, line=2)
mtext("Cumulative Change in Popularity", side=2, line=3)
lines(0:8, cumsum(out1$ur), type="l", lty=1)
lines(0:8, cumsum(out2$ur), type="l", lty=2)
lines(0:8, cumsum(out3$ur), type="l", lty=3)
lines(0:8, cumsum(out4$ur), type="l", lty=4)

legend("topright", legend=c("Model 1", "Model 2", "Model 3", "Model 4"),
       col=c(1, 2, 3, 4), lty=c(1, 2, 3, 4))

dev.copy(png, "/Users/Wallace/Desktop/Tese/fullsample.png")
dev.off()

stargazer(reg1, reg2, reg3, reg4,
          title = "Effect of Minerals Price Index on the Popularity of Australian Prime Ministers",
          align = TRUE, out = "fullsample.tex", type = "latex", omit = "leader", label = "fullsample")

#summodels <- list(reg1, reg2, reg3, reg4)
#modelsummary(summodels,
 #            stars = FALSE, statistic = c("std.error", "p.value"), output = "sumfullsample.tex")

    # The selected model on subset prior to 2000
    sel_data <- subset(all_data,year<=2000)
    reg5 <- lm(ead ~ ead_lag1 + ead_lag2 + minerals_dpct +
                      hm + leader,data=sel_data)
    reg6 <- lm(ead ~ ead_lag1 + ead_lag2 + minerals_dpct +
                      leader,data=sel_data)
    reg7 <- lm(ead ~ ead_lag1 + ead_lag2 + minerals_dpct +
                      hm,data=sel_data)
    reg8 <- lm(ead ~ ead_lag1 + ead_lag2 + minerals_dpct
                      ,data=sel_data)
    
out5 <- ur.effects(reg5, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out6 <- ur.effects(reg6, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out7 <- ur.effects(reg7, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out8 <- ur.effects(reg8, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")

par(mar=c(4, 4.5, 1, 1), mfrow=c(1, 1))
plot(c(0, 8), c(-1, 4), xlab="", ylab="", type="n", xaxt="n", bty="n", main="Unit Response Prior 2000")
axis(side=1, at=seq(0, 8, 1), labels=seq(0, 8, 1))
mtext("Quarters Since Shock", side=1, line=2)
mtext("Cumulative Change in Popularity", side=2, line=3)
lines(0:8, cumsum(out5$ur), type="l", lty=1)
lines(0:8, cumsum(out6$ur), type="l", lty=2)
lines(0:8, cumsum(out7$ur), type="l", lty=3)
lines(0:8, cumsum(out8$ur), type="l", lty=4)

legend("topright", legend=c("Model 1", "Model 2", "Model 3", "Model 4"),
       col=c(1, 2, 3, 4), lty=c(1, 2, 3, 4))

dev.copy(png, "/Users/Wallace/Desktop/Tese/unitprior2000.png")
dev.off() 

stargazer(reg5, reg6, reg7, reg8,
          title = "Effect of Minerals Price Index on the Popularity of Australian Prime Ministers in the Period Prior to 2000",
          align = TRUE, out = "unitprior2000.tex", type = "latex", omit = "leader", label = "unitprior_2000")

    # The selected model on subset post 2000
    sel_datap <- subset(all_data,year>2000)
    reg9 <- lm(ead ~ ead_lag1 + ead_lag2 +minerals_dpct +
                      hm + leader,data=sel_datap)
    reg10 <- lm(ead ~ ead_lag1 + ead_lag2 +minerals_dpct +
                      leader,data=sel_datap)
    reg11 <- lm(ead ~ ead_lag1 + ead_lag2 +minerals_dpct +
                      hm,data=sel_datap)
    reg12 <- lm(ead ~ ead_lag1 + ead_lag2 +minerals_dpct
                      ,data=sel_datap)
out9 <- ur.effects(reg9, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out10 <- ur.effects(reg10, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out11 <- ur.effects(reg11, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")
out12 <- ur.effects(reg12, lagdv1="ead_lag1", lagdv2="ead_lag2", iv="minerals_dpct")

par(mar=c(4, 4.5, 1, 1), mfrow=c(1, 1))
plot(c(0, 8), c(-1, 4), xlab="", ylab="", type="n", xaxt="n", bty="n", main="Unit Response Post 2000")
axis(side=1, at=seq(0, 8, 1), labels=seq(0, 8, 1))
mtext("Quarters Since Shock", side=1, line=2)
mtext("Cumulative Change in Popularity", side=2, line=3)
lines(0:8, cumsum(out9$ur), type="l", lty=1)
lines(0:8, cumsum(out10$ur), type="l", lty=2)
lines(0:8, cumsum(out11$ur), type="l", lty=3)
lines(0:8, cumsum(out12$ur), type="l", lty=4)

legend("topright", legend=c("Model 1", "Model 2", "Model 3", "Model 4"),
       col=c(1, 2, 3, 4), lty=c(1, 2, 3, 4))

dev.copy(png, "/Users/Wallace/Desktop/Tese/unitpost2000.png")
dev.off()

stargazer(reg9, reg10, reg11, reg12,
          title = "Effect of Minerals Price Index on the Popularity of Australian Prime Ministers in the Period Posterior to 2000",
          align = TRUE, out = "unitpost2000.tex", type = "latex", omit = "leader", label = "unitpost_2000")

````



## Take a look at the correlations between minerals and domestic and between domestic and ead

Can we spot any "anomalies"? As a first quick look we simply plot the partial correlations between our commodity, popularty and domestic economic variables in the pre- and post-2000 periods. We can see that Pré 2000, a relação minerals e growth era positiva fraca e a associação entre minerals e economic misery negativa, o que faz sentido. A relação growth-popularity era forte, o que também faz sentido.  

Pós 2000 temos uma aparente anomalia econômica  forte: minerals e misery fica positiva, e outra aparente anomalia politica que é o enfraquecimento da relação entre growth e popularidade. 

```{r correlations}

#sel_data <- subset(all_data, year < 2000)
datapre <- subset(all_data, year <2000)
corrgram(subset(datapre,select=c(minerals_dpct,okun_misery,gdp_growth,ead))
         , main = "Pre-2000")

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/corrokunprior.png")
dev.off()

#sel_data <- subset(all_data, year >= 2000)
datapos <- subset(all_data, year >=2000)
corrgram(subset(sel_data,select=c(minerals_dpct,okun_misery,gdp_growth,ead))
         , main = "Post-2000")

dev.copy(png, "/Users/Wallace/Desktop/Tese/Graphs/corrokunpost.png")
dev.off()

```

We now take a closer look at these anomalies, estiamting ADLs in the pre- and post- periods.

### Economic Anomaly: Economic Misery
```{r misery}

# Choose lag structure 
sel_data <- subset(all_data, year<2000)

# Estimate all variants of ADL(2,2) down to ADL(1,0)
iadl22 <- lm(okun_misery ~ okun_misery_lag1 + okun_misery_lag2 + 
                minerals_dpct + minerals_dpct_lag1 + minerals_dpct_lag2 + quarter, data=sel_data)
iadl21 <- lm(okun_misery ~ okun_misery_lag1 + okun_misery_lag2 +  
               minerals_dpct + minerals_dpct_lag1+ quarter, data=sel_data)
iadl20 <- lm(okun_misery ~ okun_misery_lag1 + okun_misery_lag2 +  minerals_dpct + quarter,
             data=sel_data)
iadl12 <- lm(okun_misery ~ okun_misery_lag1 +  minerals_dpct + 
               minerals_dpct_lag1 + minerals_dpct_lag2 + quarter,data=sel_data)
iadl11 <- lm(okun_misery ~ okun_misery_lag1 + minerals_dpct + minerals_dpct_lag1 + quarter,
             data=sel_data)
iadl10 <- lm(okun_misery ~ okun_misery_lag1 + minerals_dpct + quarter,
             data=sel_data)


# Collect
iadls <- list(iadl22=iadl22,iadl21=iadl21,iadl20=iadl20
			,iadl12=iadl12,iadl11=iadl11,iadl10=iadl10)

# Compute residuals
iadls.res <- lapply(iadls,residuals)

# Check F tests for restricted version of ADL(2,2)
ff <- cbind(iadl22=Inf,
  iadl21=linearHypothesis(iadl22, "minerals_dpct_lag2=0", test= "F" )$Pr[2],
  iadl20=linearHypothesis(iadl22, c("minerals_dpct_lag2=0","minerals_dpct_lag1=0"), test= "F" )$Pr[2],
  iadl12=linearHypothesis(iadl22, "okun_misery_lag2=0", test= "F" )$Pr[2],
  iadl11=linearHypothesis(iadl22, c("okun_misery_lag2=0","minerals_dpct_lag2=0"), test= "F" )$Pr[2],
  iadl10=linearHypothesis(iadl22, c("okun_misery_lag2=0","minerals_dpct_lag2=0","minerals_dpct_lag1=0"), test= "F" )$Pr[2]
)
rownames(ff)<-"ftest"

tests <- rbind(
	kpss=sapply(iadls.res,function(x){kpss.test(x)$p.value}),
	pp=sapply(iadls.res,function(x){pp.test(x)$p.value}),
	urt = sapply(iadls.res,function(x){unitrootTest(x,lags=1)@test$p.value[1]}),
	adf=sapply(iadls.res,function(x){adf.test(x)$p.value}),
	bg=sapply(iadls.res,function(x){bgtest(x~1
				,order=2,data=data.frame(res=x),fill=0)$p.value}),
	dw = sapply(adls,function(x){dwtest(lm(formula(x$call),data=x$model),
								alternative="two.sided")$p.value}) ,
	lbox=sapply(iadls.res,function(x){Box.test(x, type="Ljung-Box")$p.value}),
	arIma=sapply(iadls.res,function(x){auto.arima(x)$arma[c(1,2,6)]}),
	ftest=ff,
	bic=  sapply(iadls,BIC))

out <- data.frame(t(tests))
names(out)[grep("^V",names(out))]<-c("ar","d","ma")
 
passed <- subset(out,ftest>0.1
						&kpss>=0.1
						&pp<0.1 
						&urt<0.1
						&adf<0.1
					  &(bg>=0.1|dw>=0.1|lbox>=0.1))
ss <- which(rownames(out)==rownames(passed)[which.min(passed$bic)])
selname <- rownames(passed)[which.min(passed$bic)]
cat("\nModel with lowest BIC among those that passed all tests is ",selname,"\n",sep="")
```


## Political anomaly 
```{r popgrowth}

# Choose lag structure 
sel_datap <- subset(all_data, year>=2000)

# Estimate all variantes of ADL(2,2) down to ADL(1,0)
adl22 <- lm(ead ~ ead_lag1 + ead_lag2 + 
                gdp_growth + gdp_growth_lag1 + gdp_growth_lag2 +
                  hm + leader,data=sel_data)
adl21 <- lm(ead ~ ead_lag1 + ead_lag2 +  gdp_growth + gdp_growth_lag1 +
                  hm + leader,data=sel_data)
adl20 <- lm(ead ~ ead_lag1 + ead_lag2 +  gdp_growth +
                  hm + leader,data=sel_data)
adl12 <- lm(ead ~ ead_lag1 +  gdp_growth + gdp_growth_lag1 + 
                  gdp_growth_lag2 +
                  hm + leader,data=sel_data)
adl11 <- lm(ead ~ ead_lag1 + gdp_growth + gdp_growth_lag1 +
                  hm + leader,data=sel_data)
adl10 <- lm(ead ~ ead_lag1 + gdp_growth +
                  hm + leader,data=sel_data)


# Collect
adls <- list(adl22=adl22,adl21=adl21,adl20=adl20
			,adl12=adl12,adl11=adl11,adl10=adl10)

# Compute residuals
adls.res <- lapply(adls,residuals)

# Check F tests for restricted version of ADL(2,2)
ff <- cbind(adl22=+Inf,
  adl21=linearHypothesis(adl22, "gdp_growth_lag2=0", test= "F" )$Pr[2],
  adl20=linearHypothesis(adl22, c("gdp_growth_lag2=0","gdp_growth_lag1=0"), test= "F" )$Pr[2],
  adl12=linearHypothesis(adl22, "ead_lag2=0", test= "F" )$Pr[2],
  adl11=linearHypothesis(adl22, c("ead_lag2=0","gdp_growth_lag2=0"), test= "F" )$Pr[2],
  adl10=linearHypothesis(adl22, c("ead_lag2=0","gdp_growth_lag2=0","gdp_growth_lag1=0"), test= "F" )$Pr[2]
)
rownames(ff)<-"ftest"

## Expanded diagnostics ##
# Unit Root: 
# Kwiatkowski-Phillips-Schmidt-Shin (KPSS) test for the null hypothesis that x is level or trend stationary: should *not* reject (p>=0.1).
# Phillips-Perron test for the null hypothesis that x has a unit root: should  reject (p<0.1).
# unitrootTest: based on McKinnons's test statistics. Null is unit root, should *reject* (p<0.1)
# Augmented Dickey-Fuller test (via adf.test): null is unit root: should *reject* (p<0.1)

# Serial correlation tests:",
# Breusch–Godfrey Lagr. mult. test. h0=No serial correlation up to p=2; *not reject* (p>=0.1)
# Durbin–Watson H statistic: h0=First order autocorrelation is 0, *not reject* (p>=0.1))
# Ljung–Box (‘portmanteau’) test statistic for examining the null hypothesis of independence in a given time series. (q.test replicates stata's)
library(lmtest)
library(tseries)
library(fUnitRoots)
tests <- rbind(
	kpss=sapply(adls.res,function(x){kpss.test(x)$p.value}),
	pp=sapply(adls.res,function(x){pp.test(x)$p.value}),
	urt = sapply(adls.res,function(x){unitrootTest(x,lags=1)@test$p.value[1]}),
	adf=sapply(adls.res,function(x){adf.test(x)$p.value}),
	bg=sapply(adls.res,function(x){bgtest(x~1
				,order=2,data=data.frame(res=x),fill=0)$p.value}),
	dw = sapply(adls,function(x){dwtest(lm(formula(x$call),data=x$model),
								alternative="two.sided")$p.value}) ,
	lbox=sapply(adls.res,function(x){Box.test(x, type="Ljung-Box")$p.value}),
	arIma=sapply(adls.res,function(x){auto.arima(x)$arma[c(1,2,6)]}),
	ftest=ff,
	bic=  sapply(adls,BIC))

out <- data.frame(t(tests))
names(out)[grep("^V",names(out))]<-c("ar","d","ma")
 
passed <- subset(out,ftest>0.1
						&kpss>=0.1
						&pp<0.1 
						&urt<0.1
						&adf<0.1
						&(bg>=0.1|dw>=0.1)
						&lbox>=0.1)
 
ss <- which(rownames(out)==rownames(passed)[which.min(passed$bic)])
selname <- rownames(passed)[which.min(passed$bic)]
cat("\nModel with lowest BIC among those (",nrow(out),") that passed all tests is ",selname,"\n",sep="")

```

## Okun ~ EAD 
```{r}
# Choose lag structure 
sel_data <- subset(all_data, year<2000)

# Estimate all variants of ADL(2,2) down to ADL(1,0)
oadl22 <- lm(ead ~ ead_lag1 + ead_lag2 + 
                okun_misery + okun_misery_lag1 + okun_misery_lag2 +
                  hm + leader,data=sel_data)
oadl21 <- lm(ead ~ ead_lag1 + ead_lag2 +  okun_misery + okun_misery_lag1 +
                  hm + leader,data=sel_data)
oadl20 <- lm(ead ~ ead_lag1 + ead_lag2 +  okun_misery +
                  hm + leader,data=sel_data)
oadl12 <- lm(ead ~ ead_lag1 +  okun_misery + okun_misery_lag1 + 
                  okun_misery_lag2 +
                  hm + leader,data=sel_data)
oadl11 <- lm(ead ~ ead_lag1 + okun_misery + okun_misery_lag1 +
                  hm + leader,data=sel_data)
oadl10 <- lm(ead ~ ead_lag1 + okun_misery +
                  hm + leader,data=sel_data)


# Collect
oadls <- list(oadl22=oadl22,oadl21=oadl21,oadl20=oadl20
			,oadl12=oadl12,oadl11=oadl11,oadl10=oadl10)

# Compute residuals
oadls.res <- lapply(oadls,residuals)

# Check F tests for restricted version of ADL(2,2)
ff <- cbind(iadl22=Inf,
  oadl21=linearHypothesis(oadl22, "okun_misery_lag2=0", test= "F" )$Pr[2],
  oadl20=linearHypothesis(oadl22, c("okun_misery_lag2=0","okun_misery_lag1=0"), test= "F" )$Pr[2],
  oadl12=linearHypothesis(oadl22, "ead_lag2=0", test= "F" )$Pr[2],
  oadl11=linearHypothesis(oadl22, c("ead_lag2=0","okun_misery_lag2=0"), test= "F" )$Pr[2],
  oadl10=linearHypothesis(oadl22, c("ead_lag2=0","okun_misery_lag2=0","okun_misery_lag1=0"), test= "F" )$Pr[2]
)
rownames(ff)<-"ftest"

tests <- rbind(
	kpss=sapply(oadls.res,function(x){kpss.test(x)$p.value}),
	pp=sapply(oadls.res,function(x){pp.test(x)$p.value}),
	urt = sapply(oadls.res,function(x){unitrootTest(x,lags=1)@test$p.value[1]}),
	adf=sapply(oadls.res,function(x){adf.test(x)$p.value}),
	bg=sapply(oadls.res,function(x){bgtest(x~1
				,order=2,data=data.frame(res=x),fill=0)$p.value}),
	dw = sapply(adls,function(x){dwtest(lm(formula(x$call),data=x$model),
								alternative="two.sided")$p.value}) ,
	lbox=sapply(oadls.res,function(x){Box.test(x, type="Ljung-Box")$p.value}),
	arIma=sapply(oadls.res,function(x){auto.arima(x)$arma[c(1,2,6)]}),
	ftest=ff,
	bic=  sapply(oadls,BIC))

out <- data.frame(t(tests))
names(out)[grep("^V",names(out))]<-c("ar","d","ma")
 
passed <- subset(out,ftest>0.1
						&kpss>=0.1
						&pp<0.1 
						&urt<0.1
						&adf<0.1
					  &(bg>=0.1|dw>=0.1|lbox>=0.1))
ss <- which(rownames(out)==rownames(passed)[which.min(passed$bic)])
selname <- rownames(passed)[which.min(passed$bic)]
cat("\nModel with lowest BIC among those that passed all tests is ",selname,"\n",sep="")
```


## Tables Okun and Anomaly
```{r}
#Okun is ADL20
sel_data$quarter <- factor(sel_data$quarter)
sel_datap$quarter <- factor(sel_datap$quarter)
okunpre <- lm(okun_misery ~ okun_misery_lag1 + okun_misery_lag2 +  minerals_dpct + quarter,
             data=sel_data)
okunpos <- lm(okun_misery ~ okun_misery_lag1 + okun_misery_lag2 +  minerals_dpct + quarter,
             data=sel_datap)

stargazer(okunpre, okunpos,
          title = "Economy Misery and Minerals Prior and Post to 2000",
          align = TRUE, out = "okunprepos2000.tex", type = "latex", label = "okunprepos")


#Anomaly is ADL20
sel_data$leader <- factor(sel_data$leader)
sel_datap$leader <- factor(sel_datap$leader)
anompre <- lm(ead ~ ead_lag1 + ead_lag2 +  gdp_growth +
                  hm + leader,data=sel_data)
anompos <- lm(ead ~ ead_lag1 + ead_lag2 +  gdp_growth +
                  hm + leader,data=sel_datap)
stargazer(anompre, anompos, 
          title = "Popularity and GDP Growth Prior and Post to 2000",
          align = TRUE, out = "eadgrowprepos2000.tex", type = "latex", omit = "leader", label = "eadgrow")

#Okun em EAD ADL12
lm(ead ~ ead_lag1 +  okun_misery + okun_misery_lag1 + 
                  okun_misery_lag2 +
                  hm + leader,data=sel_data)
```

## Interaction factor 
```{r}
all_data <- all_data %>%
  mutate(post = ifelse(year >= 2000, 1, 0))
all_data$quarter <- factor(all_data$quarter)

okunfactor <- lm(okun_misery ~ okun_misery_lag2 + okun_misery_lag1 + minerals_dpct + quarter + post + minerals_dpct:post, data = all_data)
anomfactorgdp <- lm(ead ~ ead_lag1 + gdp_growth + hm + leader + post + gdp_growth:post, data=all_data)

stargazer(okunfactor,
          title = "Okun Misery Index and Commodity Price Relationship with Interaction",
          align = TRUE, out = "okunfactor.tex", type = "latex")
stargazer(anomfactorgdp,
          title = "GDP Growth and Popularity Relationship with Interaction",
          align = TRUE, out = "eadfactor.tex", type = "latex", omit = "leader")

```

# Presentation
```{r}
meanfull <- mean((all_data$minerals_dpct), na.rm = TRUE)
se_full <- sd(all_data$minerals_dpct, na.rm = TRUE) / sqrt(length(all_data$minerals_dpct[!is.na(all_data$minerals_dpct)]))
summary(meanfull)
summary(se_full)

meanpre <- mean(abs(sel_data$minerals_dpct), na.rm = TRUE)
summary(meanpre)
meanpost <- mean(abs(sel_datap$minerals_dpct), na.rm = TRUE)
summary(meanpost)


all_data$absmin <- abs(all_data$minerals_dpct)
summary(all_data$absmin)
```




# Latex - num precisa, mas deixa aqui 
## Prior 2000
```{r}
    # Um exemplo de como montar uma tabela (há outras formas de fazer) - LATEX
    # Aqui omitimos os coeffs dos pms, mas teria que acrescentar 
    # uma linha para dizer que o modelo tem pm fixed effects
    # seria bom já acrescentar também o long-run effect na mesma tabela 
    # ou entao fazer um gráfico depois com esses long-run effects...
 texreg(list(reg4,reg5,reg6)
           , include.ci = FALSE
           , custom.header = list("Pre-2000"=1:3)
           #, custom.model.names = c("3-Type","5-Type","7-Type") 
           , omit.coef = "leader"
           , custom.coef.names = c("(Intercept)","Lag. Popularity"
                                   ,"Minerals (pct. change)","Honeymoon")
           , include.pvalues = T
           , digits = 3
           , stars = c(0.01, 0.05, 0.1)
           , label = "tab:adl"
           , caption = "Coefficients of ADL(1,0)"
           , caption.above =T
           , bold = 0.1
           , ci.force = FALSE
           , file = "modelbefore.tex", type = "latex")   
```

## Post 2000
```{r}
    print(texreg(list(reg7,reg8,reg9)
           , include.ci = FALSE
           , custom.header = list("Post 2000"=1:3)
           , custom.model.names = c("3-Type","5-Type","7-Type") 
           , omit.coef = "leader"
           , custom.coef.names = c("(Intercept)","Lag. Popularity"
                                   ,"Minerals (pct. change)","Honeymoon")
           , include.pvalues = T
           , digits = 3
           , stars = c(0.01, 0.05, 0.1)
           , label = "tab:adl"
           , caption = "Coefficients of ADL(1,0)"
           , caption.above =T
           , bold = 0.1
           , ci.force = FALSE))
```

## All period
```{r}
    print(texreg(list(reg1,reg2,reg3)
           , include.ci = FALSE
           , custom.header = list("All Period"=1:3)
           , custom.model.names = c("3-Type","5-Type","7-Type") 
           , omit.coef = "leader"
           , custom.coef.names = c("(Intercept)","Lag. Popularity"
                                   ,"Minerals (pct. change)","Honeymoon")
           , include.pvalues = T
           , digits = 3
           , stars = c(0.01, 0.05, 0.1)
           , label = "tab:adl"
           , caption = "Coefficients of ADL(1,0)"
           , caption.above =T
           , bold = 0.1
           , ci.force = FALSE))
```


# long run effeects - with PM
```{r}
# Fit the dynamic linear model for the first model (reg1)
model_reg1 <- dynlm(ead ~ ead_lag1 + minerals_dpct + hm + leader, data = all_data)

coefficients_reg1 <- coef(model_reg1)
summary(model_reg1)

```


  # Pick one model to examine (and compute long run effects)
  # You can later create a list with all models and apply all these procedures to all
  # Or you can do this by hand to report the results 
  
# Residual diagnosis
## Prior 2000
```{r}
the.reg <- reg4 #escolhendo o reg4

  # Residuals diagnositcs
  par(mfrow=c(1,3))
  acf(residuals(the.reg))
  pacf(residuals(the.reg))
  hist(residuals(the.reg))

    
  source("/Users/Wallace/Desktop/Tese/Data/unit_resp_adl.R")
  out <- effects(the.reg,
                        lagdv1="ead_lag1",
                        iv="minerals_dpct")

  par(mar=c(4,4.5,1,1),mfrow=c(1,1))
  plot(c(0,8),c(-1,4),xlab="",ylab="",type="n",xaxt="n",bty="n",main="Prior to year 2000")
  axis(side=1,at=seq(0,8,1),labels=seq(0,8,1))
  mtext("Quarters Since Shock",side=1,line=2)
  mtext("Cummulative Change in Popularity",side=2,line=3)
  lines(0:8,cumsum(out$ur),type="l",lty=1)
  # pode acrescentar linhas para outros modelos no mesmo gráfico
```

## Post 2000
```{r}
the.reg <- reg4 #escolhendo o reg4

  # Residuals diagnositcs
  par(mfrow=c(1,3))
  acf(residuals(the.reg))
  pacf(residuals(the.reg))
  hist(residuals(the.reg))

    
  source("/Users/Wallace/Desktop/Tese/Data/unit_resp_adl.R")
  out <- effects(the.reg,
                        lagdv1="ead_lag1",
                        iv="minerals_dpct")

  par(mar=c(4,4.5,1,1),mfrow=c(1,1))
  plot(c(0,8),c(-1,4),xlab="",ylab="",type="n",xaxt="n",bty="n",main="Prior to year 2000")
  axis(side=1,at=seq(0,8,1),labels=seq(0,8,1))
  mtext("Quarters Since Shock",side=1,line=2)
  mtext("Cummulative Change in Popularity",side=2,line=3)
  lines(0:8,cumsum(out$ur),type="l",lty=1)
```

## Full period
```{r}
the.reg <- reg1 #escolhendo o reg4

  # Residuals diagnositcs
  par(mfrow=c(1,3))
  acf(residuals(the.reg))
  pacf(residuals(the.reg))
  hist(residuals(the.reg))

    
  source("/Users/Wallace/Desktop/Tese/Data/unit_resp_adl.R")
  out <- effects(the.reg,
                        lagdv1="ead_lag1",
                        iv="minerals_dpct")

  par(mar=c(4,4.5,1,1),mfrow=c(1,1))
  plot(c(0,8),c(-1,4),xlab="",ylab="",type="n",xaxt="n",bty="n",main="Prior to year 2000")
  axis(side=1,at=seq(0,8,1),labels=seq(0,8,1))
  mtext("Quarters Since Shock",side=1,line=2)
  mtext("Cummulative Change in Popularity",side=2,line=3)
  lines(0:8,cumsum(out$ur),type="l",lty=1)
```



# 2000 Comm X Dom - Checar se a relação entre minerals e as variaveis domesticas é diferente pre-pos 2000
```{r}
dom_all <- lm(cbind(inflation, gdp_growth, unemployment) ~ minerals_dpct, data = all_data)
summary(dom_all)
print(dom_all)

# Subset the data for years before and after 2000
before2000 <- subset(all_data, year <= 2000)
after2000 <- subset(all_data, year > 2000)

# Perform linear regression for data before 2000
modelbefore <- lm(cbind(inflation, gdp_growth, unemployment) ~ minerals_dpct, data = before2000)
descriptive_stats_before_2000 <- tidy(modelbefore)

# Perform linear regression for data after 2000
modelafter <- lm(cbind(inflation, gdp_growth, unemployment) ~ minerals_dpct, data = after2000)
descriptive_stats_after_2000 <- tidy(modelafter)

stargazer(modelbefore, 
          title = "Commodities and Domestic Variables Prior to 2000",
          align = TRUE, out = "comdompre2000.tex", type = "latex")

```


# 2000 Dom X EAD - Checar se a relacao entre domesticas e popularidade é diferente

```{r}
ead_all <- lm(cbind(inflation, gdp_growth, unemployment) ~ minerals_dpct, data = all_data)
summary(ead_all)
print(ead_all)

# Perform linear regression for data before 2000 for ead
eadbefore <- lm(cbind(inflation, gdp_growth, unemployment) ~ ead, data = before2000)
eadbefore2000 <- tidy(modelbefore)

# Perform linear regression for data after 2000
eadafter <- lm(cbind(inflation, gdp_growth, unemployment) ~ ead, data = after2000)
eadafter2000 <- tidy(modelafter)

# Print the tables
cat("Descriptive Statistics - Before 2000:\n")
print(eadbefore2000)

cat("\nDescriptive Statistics - After 2000:\n")
print(eadafter2000)

stargazer(ead_all, 
          title = "Executive Approval and Domestic Variables",
          align = TRUE, out = "eaddomall.tex", type = "latex")

```


# A relação entre Commodities e Domestic muda de um PM para outro? 

```{r}
leader_names <- c("Menzies", "Holt", "McEwen", "Gorton", "McMahon",
                  "Whitlam", "Fraser", "Hawke", "Keating", "Howard",
                  "Rudd", "Gillard", "Rudd", "Abbott", "Turnbull", "Morrison")

regression_models <- list()

for (leader_name in leader_names) {
  subset_data <- all_data[all_data$leader == leader_name, ]
  
  # Remove rows with NA values in relevant columns
  subset_data <- na.omit(subset_data[, c("gdp_growth", "inflation", "unemployment", "minerals_h")])
  
  if (nrow(subset_data) > 0) {
    model_gdp <- lm(gdp_growth ~ minerals_h, data = subset_data)
    regression_models[[paste0("gdp_", leader_name)]] <- model_gdp
    
    model_inflation <- lm(inflation ~ minerals_h, data = subset_data)
    regression_models[[paste0("inflation_", leader_name)]] <- model_inflation
    
    model_unemployment <- lm(unemployment ~ minerals_h, data = subset_data)
    regression_models[[paste0("unemployment_", leader_name)]] <- model_unemployment
  }
}

# Create an empty list to store regression models
coefficients_list <- list()

# ... your loop to create regression models ...

# Create an empty data frame to store the results
results_df <- data.frame()

# Iterate over leader names
for (leader_name in leader_names) {
  subset_data <- all_data[all_data$leader == leader_name, ]
  
  subset_data <- na.omit(subset_data)  # Remove rows with NA values
  
  if (nrow(subset_data) > 0) {
    model_gdp <- lm(gdp_growth ~ minerals_h, data = subset_data)
    model_inflation <- lm(inflation ~ minerals_h, data = subset_data)
    model_unemployment <- lm(unemployment ~ minerals_h, data = subset_data)
  
# Extract coefficients using tidy() and store in coefficients_list
    coefficients_list[[leader_name]] <- data.frame(
      Leader = leader_name,
      Constant_GDP = coef(model_gdp)[1],
      Coefficient_Minerals_GDP = coef(model_gdp)[2],
      Constant_Inflation = coef(model_inflation)[1],
      Coefficient_Minerals_Inflation = coef(model_inflation)[2],
      Constant_Unemployment = coef(model_unemployment)[1],
      Coefficient_Minerals_Unemployment = coef(model_unemployment)[2]
    )
  }
}

# Combine coefficients into a single data frame
all_coefficients <- do.call(rbind, coefficients_list)

# Print the combined coefficients data frame
print(all_coefficients)


#Results for each PM
for (leader_name in leader_names) {
  leader_results <- subset(all_coefficients, Leader == leader_name)
  print(leader_results)
}
```








